The Way Forward in Parallelizing Dynamic Languages

### 2014-05-02 talk/icooolps2014/position-paper.tex
additional cite

\paragraph{STM} provides all the same benefits as HTM except for its
performance.  It is not unusual for the overhead introduced by STM to
be between 100\% to even 1000\% \cite{cascaval08,drago11}. While STM
systems often scale very well to a big number of threads and
eventually overtake the single-threaded execution, they often provide
no benefits at all for low numbers of threads (1-8). There are some
attempts \cite{warmhoff13} that can reduce the overhead a lot, but
also scale very badly so that their benefit on more than one thread is
little.

@@

>>>>

\paragraph{STM} provides all the same benefits as HTM except for its
performance.  It is not unusual for the overhead introduced by STM to
be between 100\% to even 1000\% \cite{cascaval08,drago11}. While STM
systems often scale very well to a big number of threads and
eventually overtake the single-threaded execution, they often provide
no benefits at all for low numbers of threads (1-8). There are some
attempts \cite{warmhoff13,spear09} that can reduce the overhead a lot,
but scale badly or only for certain workloads. Often the benefits
on more than one thread are too little in real world applications.

@@

\bibitem{spear09}
  Spear, Michael F., et al. "Transactional mutex locks." \emph{SIGPLAN
    Workshop on Transactional Computing.} 2009.
